Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-02 papers/BON_VHDL/paper.tex
breaking docs

%======================================================================
\section{Introduction}
The \STs, represents heterogeneous collection of digital, analog 
and mixed signal hardware components. Embedded system complexity 
requires the need to strive for formal descriptions each component 
separatelly in order to produce specification of the \STs simulator. 
The development of complex system requires sophisticated tool and methodology 
in order to be able to complete a correct design in time.

The authors will illustrate in this paper how BON can represent a high 
level analogue mapping and will further illustrate a procedure for 
transformation from BON to VHDL-AMS. As an extremly simple example, 
we will give practical aspect of refinement from BON to VHDL-AMS,
applied on A/D convertor, in order to produce formal specification 
and software simulation.
%=====================================================================

@@

Therefore as an approach of best modelling practices, and as the notation 
based on contract design and refinement calculus, BON is the obvious choice 
for the our simulator.
Throughout this paper we will try to make this clear.  
\section{Refinement from BON to VHDL-AMS}

\subsection{Mapping between BON and VHDL-AMS}
%\todo{dragan 27/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\begin{itemize}
\item \Sc: VHDL-AMS allows hierarchical structure modeling, 
meaning that subsistems ( \ducs ), can be developed independently.
As an top-level description (informal/formal), \Sc connect all the \ducs
together to a complete design. 
\item \Clc: An  subsistem which represent \duc.
\item \Csc: describes \du. It can be identify with the primary unit (\ent) and secondary 
unit (\arch) structure in VHDL-AMS.
The \Csc's name corresponds to the name of the entity in VHDL-AMS.
\item \Ft: The feature section of the \Csc, where the mathematical 
transfer function of the component is entered, holds the same information 
as the \arch section of the VHDL-AMS.
\end{itemize}
An VHDL-AMS component are described using an \ent-\arch structure. 
The component model contains an \ent and one or more \archs. 
The \ent specifies the interface of the model to the outside world. 
In other words, \ent introduces a name, list of input/output ports 
and the definition of the generic parameters. The textual 
presentation of \ent is shown in Figure.1. 
\input{adc-entity}

>>>>

%======================================================================
\section{Introduction}
The \STs, represents heterogeneous collection of digital, analog 
and mixed signal hardware components. Embedded system complexity 
requires the need to strive for formal descriptions each component 
separatelly in order to produce specification of the \STs simulator. 
The development of complex system requires sophisticated tool and methodology 
in order to be able to complete a correct design in time.  
This article describes a refinement method from BON to VHDL-AMS
The authors will illustrate in this paper how BON can represent a high 
level analogue mapping and will further illustrate a procedure for 
transformation from BON to VHDL-AMS. As an extremly simple example, 
we will give practical aspect of refinement from BON to VHDL-AMS,
applied on A/D convertor, in order to produce formal specification 
and software simulation.
%=====================================================================

@@

Therefore as an approach of best modelling practices, and as the notation 
based on contract design and refinement calculus, BON is the obvious choice 
for the our simulator.
Throughout this paper we will try to make this clear.  
\section{Mapping between BON and VHDL-AMS}
\subsection{Static model mapping}
%\todo{dragan 27/07/2009 - Figure out : Mapping from BON  to entity/architecture structure in VHDL-ASM.}
\input{static}
\subsection{Operators-expressions mapping}
%\todo{dragan 27/07/2009 - Figure out :  VHDL-ASM as BON  represents an strongly typed language.}
This subsection summarises all relations on expressions - operators between VHDL-AMS and BON.
\input{operators}

\subsection{Type mapping}

\section{Refinement from BON to VHDL-AMS}

An VHDL-AMS component are described using an \ent-\arch structure. 
The component model contains an \ent and one or more \archs. 
The \ent specifies the interface of the model to the outside world. 
In other words, \ent introduces a name, list of input/output ports 
and the definition of the generic parameters. The textual 
presentation of \ent is shown in Figure.1. 
\input{adc-entity}
